Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-03-20 outputs/paper/paper.Rmd
directory cleaning

# Data
```{r, include=FALSE, echo=FALSE}
reduced_data <- read_csv("outputs/data/prepared_gss.csv")
reduced_data$pres16 <- factor(reduced_data$pres16, levels = c("Clinton","Trump","Other","Did not vote"))

reduced_data$Family_income <- factor(reduced_data$Family_income, 
                                     levels = c("Under $10,000","$10,000 ~ $19,999","$20,000 ~ $39,999","$40,000 ~ $59,999", 
                                                "$60,000 ~ $89,999","$90,000 ~ $129,999","$130,000 ~ $169,999","$170,000 or over"))

>>>>

# Data
```{r, include=FALSE, echo=FALSE}
# Read the reduced and cleaned data, modification done in data-preparation.r file
reduced_data <- read_csv("outputs/data/prepared_gss.csv")
reduced_data$pres16 <- factor(reduced_data$pres16, levels = c("Clinton","Trump","Other","Did not vote"))

# Change the order of variables for graphing purposes
reduced_data$Family_income <- factor(reduced_data$Family_income, 
                                     levels = c("Under $10,000","$10,000 ~ $19,999","$20,000 ~ $39,999","$40,000 ~ $59,999", 
                                                "$60,000 ~ $89,999","$90,000 ~ $129,999","$130,000 ~ $169,999","$170,000 or over"))
